Lifting CDCL to Relational Domains

### 2016-10-13 paper.tex

%===============================================================================
\begin{abstract}
%===============================================================================
%
\emph{Abstract Conflict-Driven Clause Learning} (ACDCL) is a combination of
abstract interpretation and the well-known Conflict-Driven Clause Learning 
(CDCL) algorithm that is used in SAT solvers.  ACDCL alternates between a 
model search that performs overapproximate deduction with constraint 
propagation and a conflict analysis that performs under-approximate 
abduction with heuristic choice.  
%
ACDCL has been successfully used with non-relational abstract domains 
such as intervals to improve the performance of a floating-point 
decision procedure.  Whereas the propositional level algorithms used 
in SAT solvers can be rather easily lifted from the boolean lattice to 
other non-relational domains, lifting them to relational domains is 
challenging because of relational properties of deductions and learnt clauses.
%
In this paper, we present the non-trivial adaptations of the model search and 
conflict analysis algorithms in ACDCL in order to enable the use of relational 
abstract domains.  We have implemented these algorithms inside the 2LS 
verification tool and instantiated our analysis over a template polyhedra 
domain.  We evaluate the performance of our analyzer in comparison with 
program verifiers that uses propositional-level solvers and a static 
analysis tool.  
%
Experimental evidence on a set of benchmarks drawn from bit-vector 
regression in SV-COMP'16, bit-precise software models of hardware 
circuits auto-generated from v2c tool, and several bounds checking benchmarks 
shows significant reduction in the number of decisions and backjumping iterations 
along with stronger deductions and learnt clauses aided by the richer abstract 
domains.
%
\end{abstract}
%===============================================================================
\input{introduction}
%===============================================================================

>>>>

%===============================================================================
\begin{abstract}
%===============================================================================
%
\emph{Abstract Conflict-Driven Clause Learning} (ACDCL) is a generalization
of the well-known Conflict-Driven Clause Learning (CDCL) algorithm that is
used in SAT solvers.  ACDCL alternates between a model search, which
performs overapproximate deduction with constraint propagation, and a
conflict analysis, which performs under-approximate abduction with heuristic
choice.
%
ACDCL has been successfully used with non-relational abstract domains such
as intervals to improve the performance of a floating-point decision
procedure.  Whereas the propositional reasoning used in SAT solvers can be
rather easily lifted from the boolean lattice to other non-relational
domains, lifting them to relational domains is challenging because of
relational properties of deductions and learnt clauses.
%
In this paper, we present the non-trivial adaptations of the model search
and conflict analysis algorithms in ACDCL in order to enable the use of
relational abstract domains.  We have implemented these algorithms inside
the 2LS verification tool and instantiated our analysis over a template
polyhedra domain.  We evaluate the performance of our analyzer in comparison
with program verifiers that uses propositional-level solvers and a static
analysis tool.
%
Experimental evidence on a set of benchmarks drawn from bit-vector
regression in SV-COMP'16, bit-precise software models of hardware circuits
auto-generated from v2c tool, and several bounds checking benchmarks shows
significant reduction in the number of decisions and backjumping iterations
along with stronger deductions and learnt clauses aided by the richer
abstract domains.
%
\end{abstract}
%===============================================================================
\input{introduction}
%===============================================================================
